---
title: "HW6"
output: github_document
date: "2022-11-21"
---
```{r include=FALSE}
library(tidyverse)
library(ggplot2)
set.seed(1)
```

# problem 1
```{r echo=FALSE}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```


## r²
```{r}
result <- weather_df %>% 
  modelr::bootstrap(n=5000) %>%
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x) ),
    r_results = map(models, broom::glance),
    beta_results = map(models, broom::tidy))
```


## plot of r²
```{r}
result %>%
  select(r_results) %>% 
  unnest()%>%
  ggplot(aes(x=r.squared)) + geom_density()
```
```{r}
result %>%
  select(r_results) %>% 
  unnest()%>%
  summarize(
    mean = mean(r.squared),
    se = sd(r.squared),
    "2.5-quantile" = mean(r.squared)+qnorm(0.025)*sd(r.squared),
    "97.5-quantile" = mean(r.squared)+qnorm(0.775)*sd(r.squared)
  )
```
R square is likely to be symmetrically distributed with mean 0.91, the 2.5 quantile and 97.5 quantile is 0.894 and 0.918

```{r}
beta_df <- result %>% 
  select(beta_results) %>% 
  unnest(beta_results) %>% 
  select(term, estimate) %>% 
  pivot_wider(
    names_from = term,
    values_from = estimate
  ) %>% 
  janitor::clean_names() %>% 
  unnest() %>% 
  mutate(log_value = log(intercept*tmin)) 

beta_df %>%
   ggplot(aes(x = log_value)) + geom_density()
```
```{r}
beta_df %>% 
  summarize(
    mean= mean(log_value),
    se = sd(log_value),
    "2.5-quantile" = mean(log_value)+qnorm(0.025)*sd(log_value),
    "97.5-quantile" = mean(log_value)+qnorm(0.775)*sd(log_value)
  )
```
log(β1*β2)  is likely to be symmetrically distributed with mean 2.01 . The 2.5% quantile and 97.5% quantile are 1.966 and 2.031.

# Problem 2

## Import data and tidy data
```{r warning=FALSE}
url <- 'https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv'
homicides_df <- read_csv(url(url), na = c(" ", "Unknown"))

homicides_df <- homicides_df %>% 
  mutate(city_state = str_c(city, state, sep = ", "),
         whether_solved = ifelse(
           disposition %in% c("Closed without arrest", "Open/No arrest"), 0, 1)) %>%
  filter(!city_state %in% c("Dallas, TX", "Phoenix, AZ","Kansas City, MO", "Tulsa, AL")) %>%
  filter(victim_race %in% c("White", "Black"))%>%
  filter(!victim_age == "Unknown") %>%
  mutate(victim_age = as.numeric(victim_age),
         victim_race = as.factor(victim_race),
         victim_sex = as.factor(victim_sex))
head(homicides_df)
```
Fit a logistic regression with resolved vs unresolved as the outcome and victim age, sex and race as predictors for Baltimore, MD.
```{r}
logi_baltimore= 
  homicides_df %>% 
  filter(city_state=="Baltimore, MD") %>% 
  glm(whether_solved ~ victim_age+victim_race+victim_sex, data=., family= binomial())

logi_baltimore %>%
  broom::tidy() %>%
   mutate(
    estimate = exp(estimate),
    lower = exp(confint(logi_baltimore)[,1]),
    upper = exp(confint(logi_baltimore)[,2])
   ) %>%
    filter(term == "victim_sexMale") %>%
  select(estimate, lower, upper)
```
Thus, we come to conclude that, male has 0.426 times higher odds chance of getting a resolved case compare to female.

Now, Run for all other cities
```{r message=FALSE}
# Create a function
city_odds <- function(df){
  
logi_cities <- glm(whether_solved ~ victim_age+victim_race+victim_sex,data = df , family= binomial())

logi_cities %>%
  broom::tidy() %>%
   mutate(
    estimate = exp(estimate),
    lower = exp(confint(logi_cities)[,1]),
    upper = exp(confint(logi_cities)[,2])
   ) %>%
    filter(term == "victim_sexMale") %>%
  select(estimate, lower, upper)
  
}

# apply function to cities
result_df = 
  homicides_df %>% 
  select(city_state, victim_age, victim_race, victim_sex, whether_solved)%>%
  nest(df = victim_age:whether_solved) %>%
   mutate(
    model = map(df, city_odds)
  ) %>%
  select(city_state, model)%>%
  unnest(model)
result_df
```

## Create plot
```{r}
ggplot(result_df, aes(x=fct_reorder(city_state, estimate), y=estimate))+
  geom_point()+
  geom_errorbar(aes(ymin=lower, ymax=upper))+
  labs(title = "Odds ratio of resolved homicide cases of male against female ", 
       x = "city",
       y = "odds ratio") +
  theme(axis.text.x = element_text(angle = 75, hjust = 1))
```
   




